\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-15 article.tex
small changes in previous wording

\textcolor{red}{Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships. Indeed, for a direct relationship, i.e. a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$. In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, wether there is a signal variable, i.e. a burst.}

>>>>

\textcolor{red}{Considering the short delay for a communication between neurons, slow events can be neglected to retrieve direct relationships. Indeed, for a direct relationship, i.e. a neuron firing directly implying another neuron to fire, the average time is about $1ms$ or $2ms$ while the fluorescent signal time resolution is $20ms$. In order to find out which neurons are directly related, it is only necessary to look after the burst signal, or in other words, whether the signal varies.}
